LAGOS lake depth

### 2020-03-26 figures/01_geometry.Rmd
standardize slope names

gg_slope_shape <- ggplot(data = test, 
                         aes(slope_mean, inlake_slope.y, 
                             color = shape_class)) + 
    geom_point() +
  geom_smooth(data = dplyr::filter(test, shape_class != "neither"), 
              method = "lm", se = FALSE) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "")

gg_slope_reservoir <- ggplot(data = dplyr::filter(test, !is.na(reservoir_class)), 
                             aes(slope_mean, inlake_slope.y, 
                                 color = reservoir_class)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Buffer slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "")
```

>>>>

gg_slope_shape <- ggplot(data = test, 
                         aes(slope_mean, inlake_slope.y, 
                             color = shape_class)) + 
    geom_point() +
  geom_smooth(data = dplyr::filter(test, shape_class != "neither"), 
              method = "lm", se = FALSE) +
  xlab("Nearshore slope (mean)") +
  ylab("Inlake slope") +
  labs(color = "")

gg_slope_reservoir <- ggplot(data = dplyr::filter(test, !is.na(reservoir_class)), 
                             aes(slope_mean, inlake_slope.y, 
                                 color = reservoir_class)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Nearshore slope (mean)") +
  ylab("Inlake slope") +
  labs(color = "")
```
